---
title: "Project_Code"
author: "Jared Deighton"
date: "8/31/2021"
output: html_document
---


``````{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(dplyr)
library(ggplot2)
library(deSolve)
library(tidyr)
```


````{r}

# Read in the different data, for plotting and such

Main_Data <- read_excel("Desktop/Math681/T_cell_data_used_for_modeling-edited2.xlsx", sheet = "edited full dataset", range = "B3:U17")

Weight_Data <- read_excel("Desktop/Math681/T_cell_data_used_for_modeling-edited2.xlsx", sheet = "edited full dataset", range = "B20:U34")

Formatted_Data <-read_excel("Desktop/Math681/T_cell_data_used_for_modeling-edited2.xlsx", sheet = "formatted dataset")

````

NOTES:
- Unkown parameters are set to 0, and at the bottom of the list
- IGLN ~ left inguinal lymph node
- TDLN ~ right inguinal lymph node
- Lymph flow = plasma flow / 500
- plasma volume = vascular volume
- interstitial volume = extra vascular volume
- Assuming F_bone, F_muscle, etc. = F_tissue = 1

Set the Parameters:
````{r}
# Set all the parameters
ps <- c(
        J_lung = 1843, 
        J_heart = 34.9,
        J_kidney = 87.3,
        J_brain = 1.4,
        J_muscle = 0.5,
        J_bone = 82.6,
        J_tumor = 0.6,
        J_skin = 0.6,
        J_fat = 1.6,
        J_SI = 12.9,
        J_LI = 5.2,
        J_spleen = 114,
        J_liver = 126.9,
        J_pancreas = 10,
        J_other = 86,8,
        R_kidney = 3.9,
        R_spleen = 9.8,
        R_liver = 2.5,
        E_lung = 0.84,
        F_tissue = 1,
        F_heart = 1,
        F_lung = 1,
        F_muscle = 1,
        F_skin = 1,
        F_fat = 1,
        F_bone = 1,
        F_brain = 1,
        F_kidney = 1,
        F_liver = 1,
        F_SI = 1,
        F_LI = 1,
        F_pancreas = 1,
        F_thymus = 1,
        F_spleen = 1,
        F_LN = 1,
        F_other = 1,
        F_plasma = 1,
        F_bloodcells = 1,
        F_tumor = 1,
        Q_heart = 29.9,
        Q_lung = 305,
        Q_muscle = 70.5,
        Q_skin = 22.8,
        Q_fat = 11,
        Q_bone = 12.4,
        Q_brain = 9.64,
        Q_kidney = 56.1,
        Q_liver = 8.4,
        Q_SI = 47.5,
        Q_LI = 14.1,
        Q_pancreas = 5.1,
        Q_thymus = 0.97,
        Q_spleen = 6.07,
        Q_LN = 1.35,
        Q_others = 8.91,
        Q_plasma = NA,
        Q_bloodcells = 305,
        L_heart = 36.5/500,
        L_lung = 373/500,
        L_muscle = 86.1/500,
        L_skin = 27.8/500,
        L_fat = 13.4/500,
        L_bone = 15.2/500,
        L_brain = 11.8/500,
        L_kidney = 68.5/500,
        L_liver = 10.3/500,
        L_SI = 58.1/500,
        L_LI = 17.3/500,
        L_pancreas = 6.24/500,
        L_thymus = 1.19/500,
        L_spleen = 8.18/500,
        L_LN = 1.65/500,
        L_others = 10.9/500,
        L_plasma = 373/500,
        V_heart = 0.152,
        V_lung = 	0.204,
        V_muscle = 11.3,
        V_skin = 5.02,
        V_fat = 1.98,
        V_bone = 2.82,
        V_brain = 0.485,
        V_kidney = 0.525,
        V_liver = 1.93,
        V_SI = 0.728,
        V_LI = 0.314,
        V_pancreas = 0.0970,
        V_thymus = 0.009,
        V_spleen = 0.127,
        V_LN = 0.113,
        V_others = 0.465,
        V_plasma = 0.944,
        V_whole_blood = 0.773,
        V_vascular_heart = 0.00585,
        V_vascular_lung = 0.0295,
        V_vascular_muscle = 0.249,
        V_vascular_skin = 0.188,
        V_vascular_fat = 0.0218,
        V_vascular_bone = 0.0621,
        V_vascular_brain = 0.0107,
        V_vascular_kidney = 0.0289,
        V_vascular_liver = 0.164,
        V_vascular_SI = 0.0116,
        V_vascular_LI = 0.0050,
        V_vascular_pancreas = 0.00534,
        V_vascular_thymus = 0.0005,
        V_vascular_spleen = 0.0154,
        V_vascular_others = 0.0195,
        V_extravascular_heart = 0.0217,
        V_extravascular_lung = 0.0384,
        V_extravascular_muscle = 1.47,
        V_extravascular_skin = 1.66,
        V_extravascular_fat = 0.337,
        V_extravascular_bone = 0.525,
        V_extravascular_brain = 0.0873	,
        V_extravascular_kidney = 0.0788,
        V_extravascular_liver = 0.385,
        V_extravascular_SI = 0.127,
        V_extravascular_LI = 0.0545	,
        V_extravascular_pancreas = 0.0169,
        V_extravascular_thymus = 0.00153,
        V_extravascular_spleen = 0.0254,
        V_extravascular_others = 0.0797,
        Q_tumor = 6,
        V_tumor = 0.45,
        L_tumor = 0,
        L_TDLN = 0,
        L_IGLN = 0,
        L_extravascular_kidney = 0,
        Q_tissue = 0,
        V_vascular_tissue = 0,
        V_extravascular_tissue = 0,
        V_TDLN = 0,
        V_IGLN = 0,
        J_tissue = 0
        )
````
      
      
Set up the ODEs:
````{r}
# Setting up the ODEs

# Given time values to evaluate the ODE (in hours)
times <- seq(0, 400, 1)

# Initial Conditions, these are currently unknown, set to 0.5 for now. I'm not even sure we use these or not. 
IC <- c(
        C_whole_blood = 0.5, C_vascular_lung = 0.5, C_extravascular_lung = 0.5,
        C_vascular_tissue = 0.5, C_extravascular_tissue = 0.5, C_Rvascular_tissue = 0.5,
        C_Rextravascular_tissue = 0.5, C_vascular_liver = 0.5, C_extravascular_liver = 0.5,
        C_LN = 0.5, C_IGLN = 0.5, C_TDLN = 0.5
        )


model <- function (time, init_cond, parameters) {
  with(as.list(c(init_cond, parameters)), {
    
  # WHOLE BLOOD
  dC_whole_blood <- ( -1 * (ps["Q_lung"] + ps["L_lung"]) * C_whole_blood
                     + (ps["Q_heart"] - ps["L_heart"]) * C_vascular_heart
                     + (ps["Q_kidney"] - ps["L_kidney"]) * C_vascular_kidney
                     + (ps["Q_brain"] - ps["L_brain"]) * C_vascular_brain
                     + (ps[Q_muscle] - ps["L_muscle"]) * C_vascular_muscle
                     + (ps["Q_bone"] - ps["L_bone"]) * C_vascular_bone
                     + (ps["Q_skin"] - ps["L_skin"]) * C_vascular_skin
                     + (ps["Q_fat"] - ps["L_fat"]) * C_vascular_fat
                     + ps["Q_SI"] - ps["L_SI"]
                     + ps["Q_LI"] - ps["L_LI"]
                     + ps["Q_spleen"] - ps["L_spleen"]
                     + ps["Q_pancreas"] - ps["L_pancres"]
                     + (ps["Q_liver"] - ps["L_liver"]) * C_vascular_liver
                     + (ps["Q_others"] - ps["L_others"]) * C_vascular_others
                     + ps["L_LN"]*C_LN
                     ) / ps["V_whole_blood"]
  
  # LUNGS
  ## Vascular
  dC_vascular_lung <- ( (ps["Q_lung"] + ps["L_lung"]) * C_whole_blood
                        - ps["Q_lung"] * C_vascular_lung
                        - ps["J_lung"] * C_vascular_lung * ps["V_vascular_lung"]
                        - ps["E_lung"] * C_vascular_lung * ps["V_vascular_lung"]
                        ) / ps["V_vascular_lung"]
  
  ## Extra vascular 
  dC_extravascular_lung <- ( ps["J_lung"] * C_vascular_lung *  ps["V_vascular_lung"]
                            - ps["L_lung"] * C_extravascular_lung * ps["F_lung"] 
                            ) / ps["V_extravascular_lung"]
  # TYPICAL TISSUE
  ## Vascular
  dC_vascular_tissue <- ( ps["Q_tissue"] * C_vascular_lung
                          - (ps["Q_tissue"] - ps["L_tissue"]) * C_vascular_tissue
                          - ps["J_tissue"] * C_vascular_tissue * ps["V_vascular_tissue"]
                            ) / ps["V_vascular_tissue"]
  
  ## Extra vascular
  
  dC_extravascular_tissue <- ( ps["J_tissue"] * C_vascular_tissue * ps["V_vascular_tissue"]
                              - ps["L_tissue"] * C_extravascular_tissue * ps["F_tissue"]
                              ) / ps["V_extravascular_tissue"]
  
  # TISSUE WITH RETENTION FACTOR
  
  ## Vascular
  dC_Rvascular_tissue <- ( ps["Q_tissue"] * C_vascular_lung
                          - (ps["Q_tissue"] - ps["L_tissue"]) * C_vascular_tissue
                          - ps["J_tissue"] * C_vascular_tissue * ps["V_vascular_tissue"]
                            ) / ps["V_vascular_tissue"]
  
  ## Extra vascular
  dC_Rextravascular_tissue <- ( ps["J_tissue"] * C_vascular_tissue * ps["V_vascular_tissue"]
                              - ps["L_tissue"] * (C_extravascular_tissue / ps["R_tissue"]) * ps["F_tissue"]
                              ) / ps["V_extravascular_tissue"]
  
  # LIVER
  ## Vascular
  dC_vascular_liver <- ( ps["Q_liver"] * C_vascular_lung
                         + (ps["Q_SI"] - ps["L_SI"]) * C_vascular_SI
                         + (ps["Q_LI"] - ps["L_LI"]) * C_vascular_LI
                         + (ps["Q_spleen"] - ps["L_spleen"]) * C_vascular_spleen
                         + (ps["Q_pancreas"] - ps["L_pancreas"]) * C_vascular_pancreas
                         - ((ps["Q_SI"] - ps["L_SI"])+ (ps["Q_LI"] - ps["L_LI"]) + (ps["Q_spleen"] - ps["L_spleen"]) 
                         + (ps["Q_pancreas"] - ps["L_pancreas"]) + (ps["Q_liver"] - ps["L_liver"])) * C_vascular_liver
                         - ps["J_liver"] * C_vascular_liver * ps["V_vascular_liver"]
                         ) / ps["V_vascular_liver"]
  
  ## Extra vascular
  dC_extravascular_liver <- ( ps["J_liver"] * C_vascular_liver * ps["V_vascular_liver"]
                              - ps["L_liver"] * (C_extravascular_liver / ps["R_liver"]) * ps["F_liver"]
                              ) / ps["V_extravascular_liver"]
  
  # LYMPH NODE
  dC_LN <- ( ps["F_lung"] * ps["L_lung"] * C_extravascular_lung
             + ps["F_heart"] * ps["L_heart"] * C_extravascular_heart
             + ps["L_kidney"] * ps["L_extravascular_kidney"] / ps["R_kidney"] * ps["F_kidney"]
             + ps["F_brain"] * ps["L_brain"] * C_extravascular_brain
             + C_TDLN * ps["L_TDLN"]
             + C_IgLN * ps["L_IGLN"]
             + ps["F_skin"] * ps["L_skin"] * C_extravascular_skin
             + ps["F_fat"] * ps["L_fat"] * C_extravascular_fat
             + ps["F_SI"] * ps["L_SI"] * C_extravascular_SI
             + ps["F_LI"] * ps["L_LI"] * C_extravascular_LI
             + ps["L_spleen"] * (C_extravascular_spleen / ps["R_spleen"]) * ps["F_spleen"]
             + ps["F_pancreas"] * ps["L_pancreas"] * C_extravascular_pancres
             + ps["L_liver"] * (C_extravascular_liver / ps["R_liver"]) * ps["F_liver"]
             + ps["F_others"] * ps["L_others"] * C_extravascular_others
             - ps["L_LN"] * C_LN
             ) / ps["V_LN"]
  
  # IGLN
  dC_IGLN <- ( ps["L_bone"] * ps["F_bone"] / 2 * C_extravascular_bone 
              + ps["L_muscle"] * ps["F_muscle"] / 2 * C_extravascular_muscle
              - C_IGLN * ps["L_IGLN"]
              ) / ps["V_IGLN"]
  
  # TDLN
  dC_TDLN <- ( ps["L_bone"] * ps["F_bone"] / 2 * C_extravascular_bone 
              + ps["L_muscle"] * ps["F_muscle"] / 2 * C_extravascular_muscle
              + ps["F_tumor"] * ps["L_tumor"]* C_extravascular_tumor
              - C_TDLN * ps["L_TDLN"]
              ) / ps["V_TDLN"]
  
  return(list(c(dC_whole_blood, dC_vascular_lung, dC_extravascular_lung,
                dC_vascular_tissue, dC_extravascular_tissue, dC_Rvascular_tissue,
                dC_Rextravascular_tissue, dC_vascular_liver, dC_extravascular_liver,
                dC_LN, dC_IGLN, dC_TDLN,
                init_cond)))
  })
}

````

Get the output, and plotting some solutions
```{r}
output <- ode(IC, times, model, ps)
````

Other shit:     
`````{r}
# Plots
ggplot(data=subset(Hour1, !is.na( )), aes(x=Sepal.Length)) + 
geom_bar(stat="bin")

plot(Main_Data$hour, Main_Data$lung, type = "b", xlab = "Hours", ylab = "%ID / gram")


Hour1 <- filter(Main_Data, hour == 1)
Hour1 <- Hour1[colSums(is.na(Hour1))==0]

Hour1_aves <- c()

`````


